Precise spiking motifs in neurobiological and neuromorphic data

### 2022-11-07 manuscript.tex
Update on Overleaf.

However, it was not until the study of the interaural time difference (ITD) by Gerstner in 1996~\citep{gerstner_1996} that it was discovered that this delay is not homogeneous for all neurons of the same type and species, but adapts according to their function. This ITD is a biological mechanism which allows for the azimutal localization of sound by barn owls, by organically computing the difference in arrival time of a sound between their two ears. According to Gerstner, there is a true paradox in auditory neural systems since “neural networks encode behaviourally relevant signals in the range of a few $\mu s$ with neurons that are at least one order of magnitude slower”, therefore necessarily need to play on the response time to do so. \citet{pena_2001} conducted an extended study on ITD in order to confirm this theory by identifying the coincidence detector involved, which the authors situated in the nuclear laminaris. A first hypothesis suggested that the sound coincidence was detected using stereausis, i.e. the temporal disparity between left and right cochlear loci in the owl's brain. However it was quickly set aside as the predictions did not match the measured disparities in the loci, and no variations were perceived in the nuclear laminaris for a similar sound intensity in both owl ears. The authors support a second hypothesis, that of variating axonal delays in the ipsi and contralateral cochlear nucleus magnocellularis. This second theory

Various biological experiments have thus revealed the existence of a biological axonal delay precisely adjusted according to variations of parameters in the brainstem.

@@

Over and over, myelin has been identified as one of the parameters mentioned above. Indeed, this multilaminar coating formed by the glial cells in the Vertebrates' nervous system facilitates both the neural circuit function and the behavioural performance~\cite{fields_2015}. Experiments on mammals show that myelination is directly related to learning and memory consolidation, 
%especially motor training and in enriched environments, and 
both at an early age and in older animals, due to its involvement in coupling the activity of distant neuron populations. 
%It is worth highlighting that myelination becomes increasingly important in larger brains where conductance delays are substantial and brainwave rhythms are critical; synchrony errors can lead to neuropsychiatric and neurological dysfunctions. 
% Some further studies show that oligodendrocytes may detect neuronal activity thanks to growth factors or neurotransmitters released through ion channels or via exocytosis.

%\note{\textbf{TODO amelie} section sur l'apprentissage / la plasticité des délais dans la biologie}

% (mainly based on JOBIM poster)

>>>>

However, it was not until the study of the interaural time difference (ITD) by Gerstner in 1996~\citep{gerstner_1996} that it was discovered that this delay is not homogeneous for all neurons of the same type and species, but adapts according to their function. This ITD is a biological mechanism which allows for the azimutal localization of sound by barn owls, by organically computing the difference in arrival time of a sound between their two ears. According to Gerstner, there is a true paradox in auditory neural systems since “neural networks encode behaviourally relevant signals in the range of a few $\mu s$ with neurons that are at least one order of magnitude slower”, therefore necessarily need to play on the response time to do so. \citet{pena_2001} conducted an extended study on ITD in order to confirm this theory by identifying the coincidence detector involved, which the authors situated in the nuclear laminaris. A first hypothesis suggested that the sound coincidence was detected using stereausis, i.e. the temporal disparity between left and right cochlear loci in the owl's brain. However it was quickly set aside as the predictions did not match the measured disparities in the loci, and no variations were perceived in the nuclear laminaris for a similar sound intensity in both owl ears. The authors support a second hypothesis, that of different axonal delays in the ipsi and contralateral cochlear nucleus magnocellularis. \citet{seidl_2010} experimentally seconds this hypothesis of a "coarse" regulation of delay, as the authors conclude that "variations of parameters such as axon diameter, internode distance, and others in the mammalian brainstem might be responsible for precise adjustments of physiological delays, thereby creating the framework and adjustments of the ITD detection circuit".

The experiments conducted by \citet{seidl_2010} also confirmed ... axon diameter (def \cite{gasser_1939}) + conduction velocity depending on internode distance \cite{brills_1977}

@@

Over and over, myelin has been identified as one of the parameters mentioned above. Indeed, this multilaminar coating formed by the glial cells in the Vertebrates' nervous system facilitates both the neural circuit function and the behavioural performance~\cite{fields_2015}. Experiments on mammals show that myelination is directly related to learning and memory consolidation, especially motor training and in enriched environments, and both at an early age and in older animals, due to its involvement in coupling the activity of distant neuron populations. It is worth highlighting that myelination becomes increasingly important in larger brains where conductance delays are substantial and brainwave rhythms are critical; synchrony errors can lead to neuropsychiatric and neurological dysfunctions. Some further studies show that oligodendrocytes may detect neuronal activity thanks to growth factors or neurotransmitters released through ion channels or via exocytosis.
